---
title: "Report on rtsetse phase2 testing"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
---

This is a report on the outputs produced from one run of a phase 2 test of the rtsetse model hosted here : https://andysouth.shinyapps.io/shinytse4/ .

See end of the document for the rtsetse code to repeat this run of the model locally.

Paramater values used in this run :
```{r, echo=FALSE}
#the arguments and their values passed to rtPhase2Test2
#print(unlist(lNamedArgs))
#instead perhaps I can get at all the input args from shiny ?
#print(unlist(input))
#print(unlist(isolate(reactiveValuesToList(input))))

#getting the named input vars from shiny
lNamedArgs <- isolate(reactiveValuesToList(input))

#shinyapps adds extra input vars starting ss-net* or checkbox*
#I don't want these to appear in the report
lNamedArgsSub <- lNamedArgs[ substring(names(lNamedArgs),1,3)!='ss-' & substring(names(lNamedArgs),1,8)!='checkbox' ]

#to order the params alphabetically
lNamedArgsSub <- lNamedArgsSub[ order(names(lNamedArgsSub)) ]

#trying to stop it from using sci notation
#print(unlist(lNamedArgsSub))
#works! hurrah!
print(unlist(format(lNamedArgsSub,scientific=FALSE)))

```

**Figure 1** Adult population over time summed for the whole grid.
```{r, echo=FALSE}
#rtPlotPopGrid(aRecord)
rtPlotPopGrid(v$output)
```


**Figure 2** Map of adults across the grid on final day of the simulation.
```{r, echo=FALSE}
#rtPlotMapPop(aRecord, days='final', sex='both')
rtPlotMapPop(v$output, days='final', sex='both')
```


**Figure 3** Maps of adults across the grid over the days of the simulation.
```{r, echo=FALSE}
#rtPlotMapPop(aRecord, days='all', ifManyDays='last', sex='both')
rtPlotMapPop(v$output, days='all', ifManyDays='spread', sex='both')
```


**Figure 4** Age structure over time, summed for M&F across the whole grid.
```{r, echo=FALSE}
rtPlotAgeStructure(v$output)
```


**Figure 5** Mean age of adults over time, summed for the whole grid.
```{r, echo=FALSE}
rtPlotMeanAgeGrid(v$output)
```

Code to repeat this run of the model locally :
```{r, echo=FALSE}
sCommand <- "rtPhase2Test2"
#this creates a vector of 'name=value,'
vArgs <- paste0(names(lNamedArgsSub),"=",lNamedArgsSub,", ")
#to remove the final comma & space in args list
vArgs[length(vArgs)] <- substr(vArgs[length(vArgs)],0,nchar(vArgs[length(vArgs)])-2)

cat( sCommand,"( ",vArgs," )",sep="")
#cat("\n changed \n")
```